Variability of Planetary Mass Companion 2M1207 B

### 2015-08-05 summary/letter/letter_v1.tex
one extreme case needed to be look at

\begin{figure}[h]
  \centering
  \plotone{original}
  \plotone{subtracted}
  \caption{WFC3 F160W images of 2M1207A system. Upper: original image,
    lower: residual model and primary PSF subtracted. The image of
    2M1207 B is overshadowed by the halo of the image of 2M1207A and
    can be hardly seen from the original image. With a hybrid PSF
    (residual + Tiny Tim PSF) subtraction, the image of 2M1207 B is
    clearly presented.}
  \label{fig:1}
\end{figure}
\subsection{Tiny Tim PSF Photometry}
To over come the difficulty, we make use of the Tiny Tim PSF simulator
to pursue high precision photometry under this extreme
circumstance. Tiny Tim can produce model PSF based on the filter,
spectrum of target, focus status, and the telescope jitter. One
significant advantage of Tiny Tim PSF over empirical PSF is that Tiny Tim can
produce over-sampled PSF, which makes the shifting and interpolation
rather straight forward. However, Tiny Tim model PSFs have systematic
errors. \citeauthor{Biretta2014} demonstrated that the diffraction
spikes and coma are not well simulated with Tiny Tim for WFC3 IR images.

@@

The fluxes for both 2M1207 A and B are clearly correlated with the
dithering position, which is primarily due to imperfection of the flat
field. To reduce the correlation, we normalize each group of exposures
that have the same dithering position and roll angle indivadually --
we took the median of the fluxes that were measured from these
exposures as normalization factors and devided them from every flux
measurement. 
\subsection{Uncertainty Analysis}
\begin{figure*}[h]
  \centering
  \plottwo{F125_corr}{F160_corr}
  \caption{Fluxes of the primary and the secondary is correlated with
    the ditheirng positions. Different symbols represent different
    orbits.}
  \label{fig:fig2}
\end{figure*}
\section{Result}
\begin{figure}[h]
  \centering
  \plotone{sineCurveFit}
  \caption{Normalized light curves for F125W and F160W. Red squares
    are the phtometric measurment for 2M1207 B, and gray dots are for
    2M1207 A.}
  \label{fig:3}
\end{figure}
\section{Discussion }
\begin{itemize}
\item a data-reduction pipeline is developed to obtain high precision
  photometry measurement from high contrast WFC3 IR data. For a
  contrast of $\sim 7$ magnitudes at an angular separation of
  $\sim0.7''$, we obtained photometry measurement for 2M1207 B at
  precision of about 2-3\%. 
\item time variability for 2M1207 B was discovered, the light curve of
  2M1207 B for both two colors can be fitted with a T=10.7 hr
  sinusoidal curve.
\item the atmosphere and cloud structure of 2M1207 B. How does it
  compare to the brown dwarf.
\end{itemize}
\bibliography{ref.bib}
\end{document}

>>>>

\begin{figure*}
  \centering
  \plottwo{original}{subtracted}
  \caption{WFC3 F160W images of 2M1207A system. Upper: original image,
    lower: residual model and primary PSF subtracted. The image of
    2M1207 B is overshadowed by the halo of the image of 2M1207A and
    can be hardly seen from the original image. With a hybrid PSF
    (residual + Tiny Tim PSF) subtraction, the image of 2M1207 B is
    clearly presented.}
  \label{fig:1}
\end{figure*}
\subsection{Tiny Tim PSF Photometry}
To over come the difficulty, we make use of the Tiny Tim PSF simulator
to pursue high precision photometry under this extreme
circumstance. Tiny Tim can produce model PSF based on the filter,
spectrum of target, focus status, and the telescope jitter. One
significant advantage of Tiny Tim PSF over empirical PSF is that Tiny Tim can
produce over-sampled PSF, which makes the shifting and interpolation
rather straight forward. However, Tiny Tim model PSFs have systematic
errors. \citeauthor{Biretta2014} demonstrated that the diffraction
spikes and coma are not well simulated with Tiny Tim for WFC3 IR images.

@@

The fluxes for both 2M1207 A and B are clearly correlated with the
dithering position, which is primarily due to imperfection of the flat
field. To reduce the correlation, we normalize each group of exposures
that have the same dithering position and roll angle indivadually --
we took the median of the fluxes that were measured from these
exposures as normalization factors and devided them from every flux
measurement.

\section{Result}

We obtained high signal to noise photometry series for both 2M1207 A
and B. On average, the photometric contrast is $6.52\pm0.03$ for
F125W and $5.77\pm0.02$ for F160W. The difference of F125W contrast
from 7.0 magnitude of J-band contrast \citep{Mohanty2007} and that of
F160W contrast from 5.60 magnitude of NICMOS F160W contrast
\citep{Song2006} are due to the different throughput profiles of the
filters.

Normalized light curves for both filters are presented in Figure
\ref{fig:2}. Although the light curves are relative noisy and have a
scattering of $\sim 3\%$, both F125W and F160W light curves for 2M1207
B demonstrated a significant time variability.
\begin{figure*}[h]
  \centering
  \plotone{sineCurveFit}
  \caption{Normalized F125W and F160W light curves for 2M1207 B and
    A. For companion's light curves, gray crosses are unbinned
    photometric measurements while red circles and blue squares are
    exposure-set-based binned data representing two halves of the data
  set. For F160W, green curve is least square fitted sinusoidal wave
  with period fixed to be same as the fitting result for F125W, and
  purple curve is the one with no parameter fixed in the fitting routine.}
  \label{fig:2}
\end{figure*}

\subsection{Uncertainty analysis}
\begin{itemize}
\item the source of the scattering -- 
\item flat field uncertainty -- adding artificial flat field error mask
\item validity of the variability\\
  -- both filter demonstrate similar period of variability\\
  -- split the data into two half, the trend in two halves of data
  looks similar.
  -- fix the position does not change the light curve
\item uncertainty of sinusoidal curve fit
  -- carry out a mcmc fit? is it worth doing this.
\end{itemize}

\begin{figure*}[h]
  \centering
  \plottwo{F125_corr}{F160_corr}
  \caption{Fluxes of the primary and the secondary is correlated with
    the ditheirng positions. Different symbols represent different
    orbits.}
  \label{fig:3}
\end{figure*}

\section{Discussion }
\begin{itemize}
\item a data-reduction pipeline is developed to obtain high precision
  photometry measurement from high contrast WFC3 IR data. For a
  contrast of $\sim 7$ magnitudes at an angular separation of
  $\sim0.7''$, we obtained photometry measurement for 2M1207 B at
  precision of about 2-3\%. 
\item time variability for 2M1207 B was discovered, the light curve of
  2M1207 B for both two colors can be fitted with a T=10.7 hr
  sinusoidal curve.
\item the atmosphere and cloud structure of 2M1207 B. How does it
  compare to the brown dwarf.
\end{itemize}
\bibliography{ref.bib}
\end{document}
